\section {Refinements}
\subsection{Fault Tolerance}
Since the MapReduce library is designed to help process
very large amounts of data using hundreds or thousands
of machines, the library must tolerate machine failures
gracefully.

\vspace*{8pt}%
\textbf{Worker Failure}
\vspace*{8pt}%


The master pings every worker periodically. If no response is received from a worker in a certain amount of time, the master marks the worker as failed. Any map tasks completed by the worker are reset back to their initial
idle state, and therefore become eligible for scheduling
on other workers. Similarly, any map task or reduce
task in progress on a failed worker is also reset to idle
and becomes eligible for rescheduling.
Completed map tasks are re-executed on a failure because
their output is stored on the local disk(s) of the
failed machine and is therefore inaccessible. Completed
reduce tasks do not need to be re-executed since their
output is stored in a global file system.
When a map task is executed first by worker A and
then later executed by worker B (because A failed), all
workers executing reduce tasks are notified of the reexecution.
Any reduce task that has not already read the
data from worker A will read the data from worker B.
MapReduce is resilient to large-scale worker failures.
For example, during one MapReduce operation, network
maintenance on a running cluster was causing groups of
80 machines at a time to become unreachable for several
minutes. The MapReduce mastersimply re-executed
the work done by the unreachable worker machines, and
continued to make forward progress, eventually completing
the MapReduce operation.

\vspace*{8pt}%
\textbf{Master Failure}%
\vspace*{8pt}%

It is easy to make the master write periodic checkpoints
of the master data structures described above. If the master
task dies, a new copy can be started from the last
checkpointed state. However, given that there is only a
single master, its failure is unlikely; therefore our current
implementation aborts the MapReduce computation
if the master fails. Clients can check for this condition
and retry the MapReduce operation if they desire.